Area Under Curve

### 2023-03-29 area_UC.Rmd
Update area_UC.Rmd

library(pracma)
```

@@

```{r}
comm_data %<>% mutate(month_n = as.numeric(gsub("Month","",Month.1)),
                      WetAltID = as.factor(WetAltID))
areas <- comm_data %>% group_by(WetAltID) %>% summarize(abund = trapz(month_n, size),
                                                        temp = trapz(month_n, MeanWaterTempPredC),
                                                        cc = trapz(month_n, cc),
                                                        prev = trapz(month_n, Prevalence))
```

```{r}
areas %>% ggplot(.,aes(x=abund,y=prev)) + geom_point() + geom_smooth(method = "lm")
areas %>% ggplot(.,aes(x=cc,y=prev)) + geom_point() + geom_smooth(method = "lm")
areas %>% ggplot(.,aes(x=temp,y=prev)) + geom_point() + geom_smooth(method = "lm")
```

```{r}
abund_lm <- lm(prev ~ log(abund), areas)
cc_lm <- lm(prev ~ cc, areas)
temp_lm <- lm(prev ~ temp, areas)
```

>>>>

library(pracma)
library(ggridges)
```

@@

```{r}
comm_data %<>% mutate(month_n = as.numeric(gsub("Month","",Month.1)),
                      WetAltID = as.factor(WetAltID))
areas <- comm_data %>% filter(!(WetAltID %in% c(2,18,19,20))) %>% 
  group_by(WetAltID) %>% summarize(abund = trapz(month_n, size), 
                                   temp = trapz(month_n, MeanWaterTempPredC),
                                   cc = trapz(month_n, cc),
                                   prev = trapz(month_n, Prevalence))
```

```{r}
comm_data %>% ggplot(., aes(x=Month.1,
                            y=WetAltID,
                            group=WetAltID,
                            fill=as.factor(WetAltID),
                            height = size)) +
  geom_density_ridges_gradient(show.legend = F, stat = "identity") + 
  labs(title = "Abundance over time")

comm_data %>% ggplot(., aes(x=Month.1,
                            y=WetAltID,
                            group=WetAltID,
                            fill=as.factor(WetAltID),
                            height = cc)) +
  geom_density_ridges_gradient(show.legend = F, stat = "identity") + 
  labs(title = "CC over time")

comm_data %>% ggplot(., aes(x=Month.1,
                            y=WetAltID,
                            group=WetAltID,
                            fill=as.factor(WetAltID),
                            height = MeanWaterTempPredC)) +
  geom_density_ridges_gradient(show.legend = F, stat = "identity") + 
  labs(title = "Temp over time")

comm_data %>% ggplot(., aes(x=Month.1,
                            y=WetAltID,
                            group=WetAltID,
                            fill=as.factor(WetAltID),
                            height = Prevalence)) +
  geom_density_ridges_gradient(show.legend = F, stat = "identity") + 
  labs(title = "Prevalence over time")
```

```{r}
areas %>% ggplot(.,aes(x=log(abund),y=prev)) + geom_point() + geom_smooth(method = "lm")
areas %>% ggplot(.,aes(x=cc,y=prev)) + geom_point() + geom_smooth(method = "lm")
areas %>% ggplot(.,aes(x=temp,y=prev)) + geom_point() + geom_smooth(method = "lm")
```

```{r}
abund_lm <- lm(prev ~ log(abund), areas)
cc_lm <- lm(prev ~ cc, areas)
temp_lm <- lm(prev ~ temp, areas)
summary(abund_lm)
summary(cc_lm)
summary(temp_lm)
```
